---
title: "SGPA Predict"
output: html_notebook
---

In this R markdown, I predicted the sem4 result and find RMSE and R-Square on that 


loaded packages which are required
```{r}
library(caret)
library(mlr)
library(tidyverse)
library(ggplot2)
```


reading data from SGPA.csv file
```{r}
sgpa_data <- read.csv("sgpa.csv" ,header = T)
head(sgpa_data)
```

```{r}
dim(sgpa_data)
```

changing the name of first column "i..no" to "en_no"
```{r}
names(sgpa_data)[names(sgpa_data) == "ï..No"] <- "en_no"

```

partitioning the data
```{r}
inTrain <- createDataPartition(y=sgpa_data$en_no , p=0.7, list = FALSE)
testing <- sgpa_data[-inTrain,]
training <-  sgpa_data[inTrain,]
```
```{r}
dim(testing)

```

```{r}
dim(training)
```


```{r}
lm1 <- lm(sgpa_data$sem4 ~ sgpa_data$sem1 + sgpa_data$sem2 + sgpa_data$sem3)
p1 <- predict(lm1, newdata = testing)
```

predicted values
```{r}
p1
```


summay of model 'lm1'
```{r}
summary(lm1)
```

adding column of predicted values in SGPA.csv file
```{r}
sgpa_data["prediction"] <-  p1
```

```{r}
write.csv(sgpa_data, file="sgpa_with_predicted_values.csv", append=T, row.names=F, col.names=F,  sep="," )

```

Root Mean Square Error
```{r}
RMSE(p1, sgpa_data$sem4)
```

R-Squared 
```{r}
R2(p1, sgpa_data$sem4)
```

plot a graph (prediction VS sem4)
```{r}
ggplot(sgpa_data, aes(y = sem4, x = prediction)) +
  geom_point() +
  stat_smooth()
```


